---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aarapir

Access ArcGIS online API enpoints with R

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/aarapir)](https://cran.r-project.org/package=aarapir)
<!-- badges: end -->

aarapir provides an R interface for querying and downloading publically accessible ArcGIS Online feature layers. The primary goal is to provide R users with an easy way to download features from ArcMap Online. I don't not anticipate this to be a full-fledged API to ArcGIS Online and Enterprise. See the [ArcGIS Python API](https://github.com/Esri/arcgis-python-api) for a more robust access to the ArcGIS API. This is super experimental and likely to change. This project is not associated with or supported by ESRI.

## Features

- [x] Return mapservice information

- [x] Return feature layer information

- [x] Return full feature layers (will loop requests if the maximum number of records is limited)

- [ ] Pass user query so only needed records are returned

- [ ] Return image service information

- [x] Provide interface for image or tile data

## Example


Download a point feature layer:

```{r}
library(aarapir)
## Start with a mapserver url, these typically end in "/MapServer"
## Some examples here: https://sampleserver6.arcgisonline.com/arcgis/rest/services

url <- "https://sampleserver6.arcgisonline.com/arcgis/rest/services/WindTurbines/MapServer"

## This returns a list with information from the Map Service
webserver <- service_info(url)

## We can see what feature layers are available to download
webserver$layers

## This returns a list with information about the feature layer
## id 0
layerinfo <- layer_info(webserver, 0)

## This downloads the entire feature layer and reads it into a
## simple feature dataframe
dat <- layer_download(layerinfo)
dat
```

Download a raster:

```{r}
url <- "https://landsat2.arcgis.com/arcgis/rest/services/Landsat8_Views/ImageServer"
webserver <- service_info(url)
r1 <- image_download(webserver,
                     size = "800,500",)
r1
raster::plotRGB(r1, r = 4, g = 3, b = 2, stretch = "lin",
                bgalpha = 0)
```

